---
title: Shiny Integration with RMarkdown
author: Shashank Jain
output: html_document
runtime: shiny
---
  
  #Intoduction
  
  R Markdown provides an unified authoring framework for data science, combining your code, its results, and your prose commentary. R Markdown documents are fully reproducible and support dozens of output formats, like PDFs, Word files, slideshows, and more.R Markdown provides an authoring framework for data science. You can use a single R Markdown file to both.

R Markdown integrates a number of R packages and external tools. This means that help is, by-and-large, not available through ?. Instead, as you work through this chapter, and use R Markdown in the future, keep these resources close to hand:
  
  #select input
  
  ```{r select-input}

selectInput(
  inputId = "dropdown",label = "Please make a selection",
  choices = list("Option 1"= "You have selected option 1",
                 "Option 2"= "You have selected option 2",
                 "Option 3"= "You have selected option 3"
  )
)
```

```{r- print select input}

renderText(input$dropdown)
```


# slider input

```{r select- slider}

sliderInput(inputId = "slider",label = "This is a slider",
            max = 10,min = 0,value = 5
)

sliderInput(inputId = "slider2",label = "This is a double-sided slider",
            max = 10,min = 0,value = c(4,7)
            
)
```

#checkbox input

```{r checkbox}
checkboxInput(inputId = "checkbox",label = "This is a single checkbox"
              
)

checkboxGroupInput(inputId = "checkbox2",label = "This is a multiple checkbox",
                   choices = c("A","B","C")
                   
)
```

#Radio button

```{r radio button}

radioButtons(inputId = "radiobutton",label = "This is a radio button",
             choices = c("A","B","C")
)
```

#Date input

```{r date-input}
dateInput(inputId = "date",label = "Date selector")

dateRangeInput(inputId = "daterange",label = "Please select dates",
               format = 'mm/dd/yyyy'
               
)
```

#Text input

```{r}
textInput(inputId = "text",label = "Space to enter text")

textAreaInput(inputId = "inputarea",label = "Space to enter paragraph")

passwordInput(inputId = "password",label = "Please enter your password")
```

#Render text

```{r}
renderPrint(input$text)

renderText(input$text)
```

#Render Data

```{r render- data}

DT::renderDataTable(mtcars)

```

#Plotting

```{r}
renderPlot(hist(mtcars$mpg))
```

```{r}
selectInput(inputId = "plotcolumn",label = "Choose a column",
            choices = names(mtcars)
)

sliderInput(inputId = "breaks",label = "Choose number of breaks",
            min = 5,max = 20,value = 10)
```

```{r}
renderPlot(hist(mtcars[,input$plotcolumn],breaks = input$breaks))
```


